---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 8"
author: "Tanav Thanjavuru"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 8 Exercises: 8.1, 8.2, 8.3 

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)

```



## Chapter 8 Exercises

### Problem 8.1

1.) geom_point() - Add a layer of glyphs.

2.) geom_histogram() - Add a layer of glyphs.

3.) ggplot() - Construct a graphics frame.

4.) scale_y_log10() - Change the scale for the frame

5.) ylab() - Set an axis label.

6.)facet_wrap() - Divide the frame into facets.

7.) geom_segment() - Add a layer of glyphs.

8.) xlim() - Set an axis label.

9.) facet_grid() - Divide the frame into facets.

###Problem 8.2
A.)
```{r}
ggplot(CPS85) +
 aes(x = age, colour = sex) +
 geom_density(adjust = 1.4, fill = "#0c4c8a") +
  xlim(0,30) +
   ylim(0.00,0.15)+
 scale_color_hue() +
 theme_gray() +
 facet_wrap(vars(married))

```


B.)

```{r}
ggplot(CPS85) +
 aes(x = age, y = wage, colour = sex) +
 geom_smooth(span = 0.75) +
 scale_color_hue() +
 theme_minimal() +
 facet_grid(vars(married))
```

C.)
```{r}
ggplot(CPS85) +
 aes(x = age, y = wage, colour = sex) +
  ylim(0,25)+
 geom_smooth(span = 0.75) +
 scale_color_hue() +
 theme_minimal() +
 facet_wrap(vars(sector))
```
###8.3

A.)
```{r}
ggplot(CPS85) +
 aes(x = age, y = wage) +
 geom_point(size = 1L, colour = "#000000") +
 theme_minimal()
```
B.)

```{r}
ggplot(CPS85) +
 aes(x = age, y = wage, shape = sex) +
 geom_point(size = 1L, colour = "#000000") +
 theme_minimal()
```

C.)

```{r}
ggplot(CPS85) +
 aes(x = age, y = wage, shape = sex) +
 geom_point(size = 1L, colour = "#000000") +
 theme_minimal() +
 facet_grid(vars(married), vars())
```
D.)

```{r}
ggplot(CPS85) +
 aes(x = age, y = wage, shape = married) +
 geom_point(size = 1L, colour = "#000000") +
    ylim(0,30)+
 theme_minimal()
```
