---
title: "DC Excercises: 15"
Name: "Tanav Thanjavuru"
Date: "4/5/2021"
output: html_notebook
---

```{r}
rm(list = ls())
library(mosaic)
library(tidyverse)
library(ggplot2)
library(esquisse)
library(tidyr)
```

#15.1
```{r}
ggplot(CPS85) +
 aes(x = sex, y = wage, fill = sex) +
 geom_boxplot() +
 scale_fill_hue() +
 theme_minimal()
```


#15.2
1.) The most likely height among NCHS people is about 1.62 meters because it has the highest density compared to the other heights.

2.) Based off of the graph, I would estimate that the a woman would most likely be about 1.6 meters, and for a man, would be about 1.73 meters.

3.) The BMI of a 40 year old man based off of the countour map would be about 27, and for a man the age of 70, it would be about 28-30.

#15.3

```{r}
ggplot(CPS85) +
 aes(x = educ, y = wage, colour = sex) +
 stat_smooth(method = lm) +
 geom_point(size = 0.7) +
 scale_color_hue() +
 theme_minimal() +
 ylim(0L, 15L)
```
#15.4

```{r}
ggplot(Galton) +
 aes(x = height, y = mother) +
 geom_density_2d() +
 theme_gray() +
 facet_wrap(vars(sex)) +
 xlim(57L, 75L)
```
#15.5

1.) The data indicates that that ZIP codes with high elderly populations do not tend to have high child populations.

2.) There is a relationship, although it may be weak, because a lot of the dots are around the grey area and regression line.

More data

1.) The flat line is consistent with the data, but there is a weak relationship. There are also a few outliers that are not accounted for by the line.

2.) Based off of the graph for when there are 20 zip codes, the height where the band first starts ranges from 19-27 which is a height of about 8. For the graph where there are 80 zip codes, the height ranges from about 20-24 which is a height of 4. The ratio would be 8:4 which is about 2.

3.)  Based off of the formula in 3, 1/sqrt(80) is .11 while 1/sqrt(20) is about .22. This would make the ratio about 2 to 1 which corresponds with the answer from #2.

